---
title: "Europe Gross Domestic Product (R MarkDown)</span>"
output: 
  html_document: 
    theme: yeti 
    toc: true
    toc_float: true
---

## <span style='color:#008CBA;'> 1. Check the Structure of Data
```{r}
# //////////////////////////////////
#/////Check Data Structure/////////
# ////////////////////////////////

file_path <- "C:/Users/luiss/Desktop/Europe GDP Project/Europe Gross Domestic Product (GDP) Dataset.csv"
  data <- read.csv(file_path) 
str(data)
```
```{r}
# //////////////////////////////////
# /////GDP Regressions Attempts////
# ////////////////////////////////

#How GDP in European Countries, is influenced by Immigration, and student enrollment in Education of Total population of Europe.
reg7 <- lm(gdpcountry ~ imigrtot + stdenroleduc, data=data) 
  summary(reg7)

#How GDP in European Countries, is influenced by the Emigration, and student enrollment in Education of Total population of Europe.
reg8 <- lm(gdpcountry ~ stdenroleduc + emigrtot, data=data) 
  summary(reg8)

#How GDP in European Countries, is influenced by the Emigration and Immigration of Total population of Europe.
  reg9 <- lm(gdpcountry ~ imigrtot + emigrtot, data=data) 
summary(reg9)
```

```{r}
# //////////////////////////////////
# /////Main GDP Regression ////////
# ////////////////////////////////

#How GDP in European Countries, is influenced by the Emigration, Immigration, and Student and Pupils Enrolled by all Education of Total population.
reg10 <- lm(log(gdpcountry) ~ log(imigrtot) + log(emigrtot) + log(stdenroleduc), data=data)
  summary(reg10)
```


## <span style='color:#008CBA;'> 2. T-Test for Our Independent Variables in our Main Regression
<p> If |tobs | > tα/2 =⇒ reject H0 at the α × 100% level.<p>
<p> If |tobs | ≤ tα/2 =⇒ do not reject H0. <p>
```{r}
# t-Test on the variables (Immigration):        
tobsimigrtot <- 1.0560/0.2873 # 3.6756 T-observation.
tobsimigrtot
```

```{r}
# t-Test on the variables (Emigration):
emigrtot <- (-0.6847)/0.2448 # -2.796977 T-observation.
emigrtot
```

```{r}
# t-Test on the variables (Student Enrollment Education):
stdenroleduc <- 0.6564/ 0.1174 # 5.591141 T-observation.
stdenroleduc
```
Critical Values of t-observations:
```{r}
qt(0.95,22) # 1.717144 Critical Value of significance level of 5% with 22 degrees of freedom.
qt(0.90,22) # 1.321237 Critical Value of significance level of 10% with 22 degrees of freedom.

```
<div style="text-align: justify;">
So, we can conclude that we reject the null hypothesis for all the variables, in the significance level of 5% and 10%, meaning that the variables immigration, emigration and the student enrollment on education individually explain the gross domestic product of each country in Europe.
</div>
## <span style='color:#008CBA;'> 3. F-Test for Our Independent Variables in our Main Regression 
<p>If Fobs > Fα (or p-value < α) =⇒ Reject H0.<p>
<p>If Fobs ≤ Fα (or p-value ≥ α) =⇒ Not reject H0. <p>
```{r}
# n is the number of observations (26) we have 3 variables and each of them haves 26 rows.
# k is the number of independent variables in the unrestricted model (1)
# q is the number of restrictions (2).

# Unrestricted OLS regression:
  res.ur <- lm(log(gdpcountry) ~ log(imigrtot) + log(emigrtot) + log(stdenroleduc), data=data)
    # Restricted OLS regression (without the variable stdenroleduc):
  res.r <- lm(log(gdpcountry) ~ log(stdenroleduc), data=data)
```

```{r}
# R^2 from Unrestricted:
(r2.ur <- summary(res.ur)$r.squared ) 
# R^2 from Restricted:
(r2.r <- summary(res.r)$r.squared )
```

```{r}
# F-Statistic:
 F <- ((r2.ur-r2.r)/2) / ((1-r2.ur) / (24))
 F
```

```{r}
# Calculate the critical value from the F-distribution with Significance level of 5%.
 critical_value <- qf(0.95, 1, 24) 
 critical_value 
```
<div style="text-align: justify;">
So we can conclude that we have statistical significance for the significance level of 5%, meaning that the independent variables emigration and emigration jointly explain the gross domestic product.
</div>

## <span style='color:#008CBA;'> 4. Heteroskedasticity Test in our Main Regression
 <p>• Breusch-Pagan Test #1.<p>
 <p>• White (full) Test #2. <p>
 <p>• White (special) Test #3. <p>

```{r}
# ///////////////////////////////
# /////Breusch-Pagan Test #1////
# /////////////////////////////

# H0: Presence Homoscedasticity | H1: Presence Heteroskedasticity
library(lmtest) # Automatic BP test
  bptest(reg10)
```
<div style="text-align: justify;">
So, we can conclude that we do not have evidence to suggest the presence of heteroscedasticity in the regression model, meaning the variability of the (residuals) errors changes in values across all independent variables change, because we will not reject the null hypothesis, because our p-value is higher than significance level of 5%.
</div>
```{r}
summary(lm(resid(reg10)^2 ~ log(imigrtot) + log(emigrtot)+ log(stdenroleduc), data=data)) #Observing the Heteroskedasticity individually.

```
<div style="text-align: justify;">
We identify that we have presence of heteroskedasticity only in log(imigrtot), and log(stdenroleduc) for significance level of 5%.
</div>
```{r}

# ///////////////////////////////
# /////White (Full) Test #2/////
# /////////////////////////////

# H0: Presence Homoscedasticity | H1: Presence Heteroskedasticity

reg11 <- lm(resid(reg10)^2 ~ log(imigrtot) + log(emigrtot) + log(stdenroleduc) + I(log(imigrtot)^2) + 
            I(log(emigrtot)^2) + I(log(stdenroleduc)^2) + I(log(stdenroleduc) * log(emigrtot)) +
          I(log(stdenroleduc) * log(imigrtot)) + I(log(imigrtot) * log(emigrtot)), data = data)
  summary(reg11) 
  # log(imigrtot) variable that presents heteroscedasticity. from our regression.
```

```{r}
#Compute the Linear Model observation:
length(reg10$res)*summary(reg11)$r.squared 
  bptest(reg11, data = data) 
```
<div style="text-align: justify;">
With all variables of White Full Test together, not analysed individually and we can conclude that we do not have presence of heteroskedasticity because we do not reject the null hypothesis, because the p-value is higher than the significance level of 5%.
</div>
```{r}
 #   /////////////////////
 #  //OR as Alternative//
 # /////////////////////
  
bptest(reg10, ~ log(imigrtot) + log(emigrtot) + log(stdenroleduc) + I(log(imigrtot)^2) + 
         I(log(emigrtot)^2) + I(log(stdenroleduc)^2) + I(log(stdenroleduc) * log(emigrtot)) +
         I(log(stdenroleduc) * log(imigrtot)) + I(log(imigrtot) * log(emigrtot)), data = data)
```
<div style="text-align: justify;">
With all variables of White Full Test together, not analysed individually and we can conclude that we do not have presence of heteroskedasticity because we do not reject the null hypothesis, because the p-value is higher than the significance level of 5%.
</div>
```{r}
# //////////////////////////////////
# /////White (Special) Test #3/////
# ////////////////////////////////

bptest(reg10, ~ fitted(reg10) + I(fitted(reg10)^2))

```
<div style="text-align: justify;">
With White Special Test,  we can conclude that we do not have presence of heteroskedasticity
because we do not reject the null hypothesis, because the p-value is higher than the significance level of 5%.
</div>

## <span style='color:#008CBA;'> 5. Robust Estimation

```{r}
# //////////////////////////////////
# /////Robust Estimation///////////
# ////////////////////////////////

library(lmtest); library(car)
reg10 <- lm(log(gdpcountry) ~ log(imigrtot) + log(emigrtot) + log(stdenroleduc), data=data)
# Usual SE:
coeftest(reg10)
# Refined White heteroscedasticity-robust SE:
coeftest(reg10, vcov=hccm)

```
<div style="text-align: justify;">
Observing the the final outputs by using the heteroscedasticity of Robust Estimation on Standard Errors and the Usual Standard Errors of the coefficients, we can conclude that we have statistical significance for both variables log(imigrtot) & log(stdenroleduc) meaning that the will not have presence of heteroscedasticity because we reject in both scenarios (heteroscedasticity of Robust Estimation) on Standard Errors and the Usual Standard Errors) for the significance level of 5%, but for the variable log(emigrtot) we have presence of heteroscedasticity because we do not reject in the coefficients of the Standard Error for the significance level of 5% but when we apply the Robust Estimation we only reject for the significance level of 10%.
</div>


## <span style='color:#008CBA;'> 6. Chow Test

```{r}
# /////////////////////////////////
# /////Chow Test//////////////////  
# ///////////////////////////////

# Expectancy Births Over 80 Years = 1 & Expectancy Births Lower 80 Years = 0
# Country of Europe haves Euro Coin = 1 & Country of Europe does not haves Euro Coin = 0

# Chow Test (What is the partial Effect of having Euro Coins in Immigration, Emigration, and Student Enrollment on Education considering all the countries that have Expectancy births over 80 Years)
reg15 <- lm(log(gdpcountry) ~ eurozone * log(imigrtot) + eurozone * log(emigrtot)+ eurozone * log(stdenroleduc), data=data, subset=(expbirthd==1))
summary(reg15)

#So, we just only use the value of p-value meaning that the explanatory variables explain the gross domestic product of European countries for the significance level of 5%.

library(car)
# linearHypothesis(reg15, matchCoefs(reg15, "eurozone"))
```
<div style="text-align: justify;">
Meaning having the euro coin highly contributes on gross domestic products, the economy growth of Europe Countries according the factors immigration, emigration, and for student enrollment on education.
</div>